

#Importing libraries
```{r}
library(pheatmap)
library(ggplot2)
library(factoextra)
```

```{r}
data1 = read.csv("Data metabiloites 12-05-24.csv",sep = ",")  # Original data
```


```{r}
head(data1)
```

```{r}
data = read.csv2("Data metabiloites 12-05-24.csv",sep = ",",row.names = 1) # modified data
```

```{r}
data
```
The columns was character so I had to change their data types to numeric

```{r}
data$HWHS = as.numeric(data$HWHS)
data$HSLW = as.numeric(data$HSLW)
data$LSHW = as.numeric(data$LSHW)
data$LSLW = as.numeric(data$LSLW)
```
```{r}
data
```

```{r}
dim(data)
```
```{r}
data_mat = t(data)

corr = cor(data_mat)
```

```{r}
pheatmap(data_mat,fontsize_row = 7 ,fontsize_col = 7,main = "Correlation between Metabolites & Treatments")
```
This heat map shows the correlation between treatmen and metabolites


```{r}
pheatmap(corr,fontsize_row = 7 ,fontsize_col = 7,main = "Correlation between Metabolites in our data")
```
This heat map shows the correlation between the metabolites, We could see the that the group on the upper left side are strongly correlated with each other.


Preparing the data for the principal component analysis


We need to exclude the categorical variable to be able to calculate the PCA

```{r}
head(data1)
```
Exclude the Sample column

```{r}
sample = data1[,-1]
```


```{r}
sample
```


```{r}
my_pca = prcomp(sample,scale= TRUE)
```


```{r}
my_pca
```

we will use ggbiplot
```{r}
library(ggbiplot)
library(ggplot2)
```


```{r}
ggbiplot(my_pca,obs.scale = 1 ,var.scale = 3 ,groups = colnames(data_mat),ellipse = TRUE,circle = TRUE,ellipse.prob = 0.50,point.size = 2,var.axes = FALSE,varname.abbrev = TRUE)+ggtitle("This graph study the variation of our Metabolites according to treatment")+theme(text = element_text(size = 10))
```

The graph abouve shows the variation in metabolites according to the type of treatment
